---
title: "Capital-Labor elasticity of substitution"
author: "Fabien Petit"
date: "24/05/2019"
output: github_document
---

```{r Init, include = FALSE}

# Define required packages
library(dplyr)
library(reshape2)
library(ggplot2)

# Define paths
loc_final = file.path("data", "final")

```

## Methodology

I estimate the elasticity of substitution between capital and labor using the methodology of Leon-Ledesma, McAdam & Willman (2013). Estimation are done for France and United States between 1970 and 2010.

## Estimation (PWT only)

```{r Load data}

pwt = read.csv(file.path(loc_final, "pwt.csv"), header = TRUE) %>% 
  subset(Country %in% c("France", "United States") & Year %in% c(1970:2010) & i_labsh2 == 1) %>% 
  select("Country", "Year", "pop", "emp", "avh", "rnna", "labsh")

head(pwt)

```

The variables from the **Penn World Table 9.1** are the following :

* *pop* : Population (in millions.)
* *emp* : Number of persons engaged (in millions)
* *avh* : Average annual hours worked by persons engaged
* *rnna* : Capital stock at constant 2011 national prices (in mil. 2011US$)
* *labsh* : Share of labour compensation in GDP at current national prices

Following the methodology of Leon-Ledesma, McAdam & Willman (2013), I estimate the following equation :

$$\ln k_t = \alpha - \frac{\sigma}{1-\sigma} \ln \Theta_t + \left( a_L-a_K\right)t + \varepsilon_t$$

Therefore, I need to compute the capital-to-labor ratio $k_t$ and the capital-to-labor income ratio $\Theta_t$.

```{r Variable computation}

# Capital in the economy (K)
pwt$K = pwt$rnna
# Capital in the economy (K) // Corrected for hours worked
pwt$K.avh_correct = pwt$rnna / pwt$avh

# Capital-to-labor ratio (k)
pwt$k = pwt$K/pwt$emp
# Capital-to-labor ratio (k) // Corrected for hours workers
pwt$k.avh_correct = pwt$K.avh_correct/pwt$emp

# Capital-to-labor income ratio (THETA)
pwt$THETA = (1-pwt$labsh)/pwt$labsh

```

I normalize the capital-to-labor ratio to the initial year (i.e. 1970).

```{r Normalization}

pwt = pwt %>% 
  group_by(Country) %>% 
  mutate(k_nor = k / first(k),
         k_nor.avh_correct = k.avh_correct / first(k.avh_correct)) %>% 
  ungroup()

```


```{r Plot k}

pwt %>% select("Country", "Year", "k_nor", "k_nor.avh_correct") %>% 
  melt(id.vars = c("Country", "Year")) %>% 
  ggplot(aes(x = Year, y = value, color = variable)) +
  geom_line(size = .5) +
  facet_wrap(Country ~ ., dir = "v") +
  theme_classic(base_size = 14) +
  labs(x = "Year", y = "")

```













