% !TeX spellcheck = en_US

%% STEP 1 : Announce your topic ONE PARAGRAPH ONLY

The labor income share is often assumed as constant by the economists. However, it has decreased during the last decades in OECD countries as emphasized by \cite{Karabarbounis2014} (see also \citealt{Elsby2013} for a detailed analysis of the US labor share).
At the same time, high-income countries such as France and the United States have experienced a population aging related to the existence of the larger cohort of the \textit{baby-boomers}. Aging population and its consequences on macroeconomic variables have recently received an increasing interest; see \cite{Sheiner2014}.
Yet, the literature has paid little attention to the impact of population dynamics on the labor share. The aging of the population and the declining labor share, in high-income countries, raise the question of whether the age structure of the population is a factor affecting the way in which national income is allocated between labor and capital.
Moreover, variations of the demographic structure may also affect public policy by changing welfare state preferences. Many authors have shown the existence of intergenerational conflicts over public budget allocation (see, for example, \citealt{Busemeyer2009}; \citealt{Sorensen2013}). Public policy determines labor market institutions which are key determinants of wage and employment and therefore the labor share.
To the best of my knowledge, this paper is the first to investigate the long-run relationship between the demographic dynamics and the labor share through the age-related conflict in public policy which determines the rules of the wage bargaining.

%% STEP 2 : Extended abstract and guideline of the paper (300 words ?)

%% Theoretical framework
I start by presenting a theoretical framework which links the age structure of the population to the labor share. I use a two-period overlapping generations (OLG) model with two types of individuals: young and old. Young individuals supply labor and earn a labor income while old households earn capital income, the return of their savings.
% Public policy
The government levies taxes on both incomes and uses them to provide unemployment benefits and fund health spending on the elderly. The public budget allocation is a source of intergenerational conflict because any welfare improvement for a generation is done at the expense of the other generation. Public policy is determined through voting. The larger is a generation with respect to the other, the stronger is its political power and therefore the closer to its ideal public policy is this generation. Youth desire more redistribution and unemployment benefits.
% Wage bargaining
Meanwhile, the representative labor union bargains with the representative firm over wages. The out-of-work options of young agents are positively affected by the level of unemployment benefits but negatively by the tax rate. These options enable the representative union to bargain greater wages. However, greater wages reduce the labor demand of the representative firm and thus increases the capital-per-worker and output-per-worker. The labor share can be defined as the ratio between the wage rate and output-per-worker. Consequently, the effect of greater wages on the labor share depends on the value of the capital-labor elasticity of substitution.
% Link
The equilibrium is determined by the interaction of the voting and the wage bargaining. The total effect of demographic dynamics on the labor share passes through three variables: the capital stock determined by the savings of the previous young generation; the labor supply which is taken into account in the wage bargaining; and the youth political power that defines the level of the out-of-work option and thus the ability of workers to increase their wages. However, the total effect is ambiguous and depends on parameter values.

%% Quantitative analysis
% Mechanisms
To deal with the ambiguity of the qualitative effect, I provide a quantitative analysis for France and the United-States. The calibration of the parameters leads to an elasticity of substitution between capital and labor greater than one. Both input factors are gross substitutes. The model is able to replicate the data over the last decades and predicts a slight rise of the labor share due to the aging of the baby-boomers' cohort. This cohort drives the public policy agenda and hence the labor share. When the baby-boomers are young, their massive entrance in the labor market increases the labor supply. They also shape institutions in their favor through the voting process, leading to greater wages. As a response, firms shift away from labor toward capital to thwart the workers' ability to grab part of the income. Thus, the labor share declines. Once this generation becomes old, the mechanism is reversed. However, the expected increase in the labor share is dampened by the capital accumulation fostered by the extensive savings of the baby-boomers. In the very long run, the labor share decreases with the aging of the population.

% Counterfactual, decomposition and dicussion
I also quantify the role of each determinant and channel. The determinants of the demographic dynamics' impact on the labor share are the population growth and the survival rate, i.e. the life expectancy. The rising survival rate is the dominant explanatory factor in both countries. Then, the age structure of the population affects the labor share in two different ways: directly through the labor supply and the capital accumulation, and indirectly through the public policy. Model predictions suggest that the indirect channel should play a considerable role in the next decades due to the retirement of the baby-boomers.

% Discussion
Lastly, two aspects are worth noting. First, even though baby-boomers appear as income losers over the last decades because the labor share has fallen, they were actually the winners once net income is considered due to the implementation of a redistributive public policy. Once they retire, they are still the winners of public budget allocation's intergenerational conflict because their children fund their health spending. Second, I find that an increase of the retirement age in the next decades should lead to a decline of the labor share due to capital over-accumulation, but an increase in the very long-run.

%%% OLD VERSION
%% STEP 3 : What the paper does & how it fills the gap or solves the problem that you have identified
%% What the paper does
%In the continuity of their approach, I investigate the negative correlation between the aging population and the labor share. I consider an OLG model in a framework with probabilistic voting and wage bargaining. In addition of a change in capital stock, the labor share is also affected by outside options in the wage bargaining. These outside options are determined through the public policy where it exists an age-related conflict between young and old. 
%I realize a quantitative analysis for France and the United-States. I also perform an aging-effect decomposition to analyze to which extent demographic determinants affect the labor share and through which channels. As \cite{Gonzalez-Eiras2012}, there are two determinants of demographic dynamics: population growth and survival rate (i.e. life expectancy). But also two transmission mechanisms: a direct one that is reflected in capital accumulation and labor supply ; and an indirect one through the public policy instruments.
%
%% Preview of the results
%Quantitative results suggest that the model is able to replicate long-run dynamics of the labor share in France and United-States. Demographic dynamics explain relatively better the French data pattern with respect to US data. This is due to the larger size of the welfare state and the greater disparity of cohort sizes in France. 
%The declining labor share of the past decades was mainly driven by the baby-boomers cohort. Model predictions suggest that the aging of the baby-boomers cohort should generate a modest increase of the labor share for next decades.
%I find that the rising survival rate is a much more explaining factor of labor share dynamics than the declining population growth. I also find that the direct effect dominates the indirect one until 2010 and is dominated thereafter.
%Although the labor income share was declining due to policies implemented by baby-boomers, they were not the losers over this period because they extracted part of the income of the elderly through redistribution.

%% STEP 3 : Review previous research on your topic RELATED TO WHAT YOU HAVE DONE ! To which part of the literature you add something ?

%% Labor share
This paper is related to the extensive literature on the labor share (see, for example, \citealt{Blanchard1997}; \citealt{Caballero1998}; \citealt{Acemoglu2003}; \citealt{Karabarbounis2014}; \citealt{Autor2019}). Multiple determinants have been analyzed by economists to explain its decline over the past decades, notably the role of institutions and the biased technical change.\footnote{Although the globalization has also recently received sizable research interest as a determinant of the labor share (see, for example, \citealt{Jayadev2007}; \citealt{Pica2010}; \citealt{Young2018}; and \citealt{Autor2019}).}
The institutional context argument was first put forward by \cite{Blanchard1997} to explain the persistence of shocks to the labor market. In principle, the adverse supply shocks of the 1970s should have had an impact on employment and the labor share only in the short run. Due to labor market institutions, such as adjustment costs, these shocks generated long lags in labor demand and thereby their persistence in the long-run.
%This argument relies on the previous work of \cite{Bentolila1990} who show the concern of firing cost in the firms' ability to hire and fire. Such a labor market institution constrains the firms and leads to increase the labor share in the short run. 
In addition to adjustment costs, \cite{Bentolila2003} also highlight the role of workers' bargaining power to explain the gap between the marginal product of labor and the wage.
These pro-labor income institutions are a burden to firms because they limit the firms' ability to optimize input factors' allocation but also because they enable the workers to obtain a high income share in the short-run. \cite{Caballero1998} incorporate the long-run response of firms in order to thwart workers empowerment. This response is the substitution of labor with capital through biased technical change.\footnote{\cite{Acemoglu2002} shows that factor abundance and factor prices are key determinants of the direction toward which factor the technical change is biased. In line with this result, \cite{Karabarbounis2014} show that the decrease in the relative price of investment goods induced firms to shift away from labor and toward capital.
%The price of investment goods is relative to the one of consumption goods in their paper. However, it can also be interpreted as the relative price of capital with respect to labor since wages are correlated with the consumer price level.
} Others have developed models with factor-saving innovation (see, for example, \citealt{Zuleta2008}; \citealt{Peretto2013}).
I do not incorporate any biased technical change in the model in order to analyze the role of the demographic dynamics. I show that the model is able to replicate labor share's dynamics without biased technical change. Therefore, it suggests that biased technical change may be the firms' response to the workers empowerment fostered by changes in the age structure of the population. I use the argument developed by \cite{Caballero1998} by looking at an upstream step to determine the reasons of such a labor market institutional context. I claim that labor market institutions are the result of the aggregation of public policy preferences.

% Public policy preferences
This paper relies on recent empirical studies showing that public policy preferences are likely to change over the life-cycle. Because the youth and the elderly do not benefit from the same public policy instruments nor have the same income sources (see, for example, \citealt{Busemeyer2009}; \citealt{Sorensen2013}).\footnote{\cite{Sorensen2013} uses cross-sectional survey data for 22 countries from four Role of Government surveys (1985, 1990, 1996 and 200) of the International Social Survey Program (ISSP). He shows that elderly people desire less spending in education while they are in support of more in health and pension. But he claims that these life-cycle effects are quite small. \cite{Busemeyer2009} use cross-sectional survey data for 14 OECD countries from the 1996 ISSP Role of Government dataset. On the contrary, they find sizable age-related differences in public policy preferences.} Although these studies disagree on the magnitude of the conflict, they all claim that such a conflict does exist. They also agree on the magnitude heterogeneity across countries. \cite{Jager2016} find a negative long-run relationship between population aging and public investment because older individuals discount more future payoffs with respect to young individuals.\footnote{\cite{Jager2016} use panel data of 19 OECD countries between 1971 and 2007. See also, \cite{Harrison2002}; \cite{Read2004}, for estimations of discount rates. It is also worth mentioning the recent empirical study of \cite{Huffman2017} in which they decompose the characteristics of time discounting in old population.} 
I make use of recent findings on life-cycle public policy preferences to generate an inter-generational conflict over the public budget allocation. For simplicity, I summarize it on two dimensions: the unemployment benefits and the health spending. Although the unemployment benefits are necessary to generate an interaction with the labor market through the wage bargaining. Health spending could be replaced by any type of government spending that benefits the elderly.

%% Politico-Economic equilibrium
This paper also relates to the literature on politico-economic models. This literature follows the work of \cite{Lindbeck1987} on probabilistic voting. These models are useful to examine the relationship between redistribution policies and growth.\footnote{See, for example, \cite{Alesina1994}; \cite{Persson1994}; \cite{Krusell1997}.} The first models were rather focused on intra-generational government budget allocation conflicts, while recent papers such as \cite{Lancia2012} are concerned with inter-generational conflicts. \cite{Lancia2012} develop a politico-economic equilibrium model in which aging has two opposite effects on growth. On one hand, it generates incentives for human capital accumulation and innovation, on the other, it increases the political weight of the elderly who are against innovation and makes policies more difficult to implement.\footnote{Their OLG model has three types of agents: young, adult and old. The economic growth is determined by two components: human capital growth and total factor productivity growth. First, young agents inherit the average human capital level of their parents and decide to invest on their education level. The higher is the expected life expectancy, the greater is the incentive to educate. Investing in education increases human capital. Second, all agents vote to determine the innovation public policy that fosters total factor productivity. This investment is done at the cost of public pensions. Thus, elderly are necessary opposed to innovation. When both, young and adults, are net winners from public investment policy, they form a coalition in the political process to adopt such a policy.} 
With the same type of conflict on transfers to retired old households and public investment, \cite{Gonzalez-Eiras2012} analyze implications for per-capita growth.\footnote{However, they also endogenize the retirement age in a politico-economic equilibrium.} My approach is closely linked to theirs but applied to the labor share. They distinguish two effects: a direct one through the savings rate, labor supply and capital accumulation, and an indirect one through the age-related conflict to determine taxes, government spending and the retirement age. They predict an increase in the tax rate and the retirement age in OECD countries to offset population aging which should boost per-capita growth. I use the same decomposition into the direct and indirect channels. I also decompose the aging of population in the decline in population growth and the increase in the survival rate, i.e. the life-expectancy.
I show that the age structure of the population affects factor shares. Yet, most of the papers that look at the impact of population aging on the economic growth use a Cobb-Douglas production function where factor shares are constant. Therefore, I suggest that some conclusions should be reconsider inline with this mechanism.

%% Aging on macro variables
An interest in the impact of demographic dynamics on economic variables is not new. Many authors have looked at it at the micro and macro-levels.\footnote{see \cite{Clark1978} for a survey; and \cite{Bloom2016} for a recent survey of the determinants of population aging.} 
This phenomenon presents serious challenges in many fields of the economy. Some authors have examined its impact on economic growth (see \citealt{VanGroezen2005}; \citealt{Soares2005}; \citealt{Bloom2010}; \citealt{Lee2010}). Others have investigated the sustainability of pension systems in such a context (see \citealt{Ono2003}; \citealt{DelaCroix2013}; \citealt{Philipov2014}) and discussed the optimality and feasibility of pension reforms (see \citealt{Pecchenino1997}; \citealt{Sinn2003}). Related to the pension issue, the legal age of retirement is also probed (see \citealt{Futagami2001}; \citealt{Dedry2017}). Despite the existing literature on population aging, the impact on the income allocation between capital and labor has been understudied. To the best of my knowledge, \cite{Schmidt2013} is the only existing paper looking at the impact of population aging on the labor share. They use an OLG model with a pension system to show that an aging population leads to more saving and hence more capital. For a capital-labor elasticity of substitution greater (resp. smaller) than unity, the effect on the labor share is negative (resp. positive). Their paper points out a link between the population aging and the labor share through capital accumulation.\footnote{They also show that population aging reduces the labor share in a small economy with perfect capital mobility, regardless of the value of capital-labor elasticity of substitution. Households invest abroad because domestic interest rates fall. As a result, the increasing net foreign assets income shrinks the labor share.} My paper includes this mechanism and reaches the same conclusions on it. However, I add a new mechanism through the inter-generational conflict over public budget allocation.

%% Capital-labor elasticity of substitution ?

%% Limits ?

The two main hypothesis of the paper are about the elasticity of substitution between capital and labor and the right-to-manage specification for the wage bargaining. Recent estimates suggest that this elasticity may be greater than one (see \citealt{Karabarbounis2014})\footnote{\cite{Caballero1998} also use a relatively high value of the capital-labor elasticity of substitution, about 6.00, to simulate French data.} but an other part of the literature has found it below one, particularly for the United-States (see, for example, \citealt{Antras2004}; \citealt{Chirinko2008}). 
Moreover, I do not include any form of biased technical change within the model. This is voluntary in order to develop an other theory on the labor share's decline based on demographic dynamics. It could be the case that biased technical change is also driven by demographic dynamics through the \textit{grability} of workers to seize part of the rent. This grability may be generated by some cohorts which are sufficiently numerous to shape labor market institutions in their favor and therefore in favor of labor.

%% FINAL STEP : Describe the organization of your paper

The paper is organized as follows. Section \ref{sec:model} presents the theoretical framework. Section \ref{sec:quantitative_analysis} provides the quantitative analysis. It starts with the analysis of the model's predictions and mechanisms. I then perform an aging-effect decomposition with counterfactual simulations. Section \ref{sec:discussion} discusses some results of the paper. Section \ref{sec:conclusion} concludes.







%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%% OLD VERSION of the literature
%%%% Labor share literature
%%This paper is related to the extensive literature on the labor share. Multiple determinants have been analyzed by economists to explain its decline. The three main explaining factors are institutions, biased technical change and globalization. Furthermore, these factors are closely linked.
%%% Institutions
%%Institutions affect the labor share through the labor market structure. \cite{Blanchard1997} points out the role played by institutions in the persistence of shocks. He references and examines the adverse shifts in labor supply during the 1970s and in labor demand during the 1980s that occurred in Continental European countries. In principle, adverse supply shocks of the 1970s would have had an impact on employment and the labor share but only in the short run. Due to labor market institutions, such as adjustment costs, these shocks generate long lags in labor demand and thereby their persistence in the long-run. \cite{Bentolila1990} show the concern of firing cost in the firms' ability to hire and fire. Such a labor market institution constrains the firms and leads to increase the labor share in the short run. In addition to adjustment costs, \cite{Bentolila2003} also highlight the role of workers' bargaining power to explain the gap between the marginal product of labor and the wage.
%%% To summarize, these authors have shown that labor market institutions increase the labor share, at least in the short run.
%%
%%% Biased technical change
%%Biased technical change is also a determinant of the labor share. \cite{Acemoglu2002} argues that endogenous technical change can be directed towards one factor or an other, thus generating a bias. The targeted factor is determined by two competing effects: the price effect and the market size effect. The former favors the scarce factor while the latter promotes the abundant factor. The relative strength of those two effects are closely linked to the value of the elasticity of substitution between factors. Therefore, factor abundance and factor prices are determinant of the labor share. In line with this result, \cite{Karabarbounis2014} show that the decrease in the relative price of investment goods induced firms to shift away from labor and toward capital. Others have developed models with factor-saving innovation (see, for example, \citealt{Zuleta2008}; \citealt{Peretto2013}).
%%
%%% Caballero and Hammour (1998) : link institutions and BTC
%%As previously mentioned, the determinants of the labor share are closely linked. \cite{Caballero1998} show the impact of labor market institutions on the capital accumulation. They argue that biased technical change is a response of firms in the long run to the ability of workers to obtain a high income share in the short run. This ability is owing to pro-labor income institutions. These institutions allow workers to grab part of the capital income in the short run. In order to thwart this appropriation, firms substitute labor with capital in the long run.
%%
%%% Globalization
%%Some authors have shown that globalization has a negative effect on the labor share through different aspects. \cite{Elsby2013} mention offshoring as one of them. Due to trade liberalization, labor intensive components of the US supply chain are outsourced abroad where labor factor is cheaper. \cite{Krugman2008} and \cite{Bassanini2014} also support this argument.\footnote{However, \cite{Krugman2008} argues that offshoring has a modest impact because developing countries are specialized in niche industries. But also due to vertical specialization industries, meaning that only simplest tasks are performed abroad and thereafter final products are assembled in developed countries.} An other explanation belongs to trade and capital account openness. The increasing mobility of goods and capital has negative consequences on the labor share. By either decreasing directly the wage bargaining power (see \citealt{Jayadev2007} and \citealt{Young2018}) or giving incentive to implement labor market reforms due to capital competition between countries as emphasized by \cite{Pica2010}. These reforms then reduces wage bargaining power. Finally, a more recent reasoning is developed by \cite{Autor2019} about ``superstar firms''. Due to globalization, the most productive firms dominates their market. These superstar firms are characterized by high markups and low labor share. They reduce the aggregated labor share because they represent a growing share of the output.
%
%%% Demographic dynamics literature
%%This paper is also related to the literature on demographic dynamics and their implications on economic variables. This topic is not new in itself, many authors have already looked at it at micro and macro-levels (see \citealt{Clark1978} for a survey). The renewal is mainly motivated by the current and expected shift of the population structure in high-income countries.\footnote{See \cite{Bloom2016} for a recent survey of the determinants of population aging.} This phenomenon presents serious challenges in many fields of the economy. Some authors have examined its impact on economic growth (see \citealt{VanGroezen2005}; \citealt{Soares2005}; \citealt{Bloom2010}; \citealt{Lee2010}). Others have investigated the sustainability of pension systems in such a context (see \citealt{Ono2003}; \citealt{DelaCroix2013}; \citealt{Philipov2014}) and discussed about the optimality and feasibility of pension reforms (see \citealt{Pecchenino1997}; \citealt{Sinn2003}). Related to the pension issue, the legal age of retirement is also probed (see \citealt{Futagami2001}; \citealt{Dedry2017}).
%
%%% Sorensen, Busemeyer and Jager
%%Besides all these challenges raised by population aging, the public budget allocation remains the main underlying political issue. This issue is related to the presence of an age-related conflict within the public policy. The youth and their elderly do not benefit from the same public policy instruments neither have the same type of income. Therefore, preferences are likely to change over the life-cycle. On one hand, \cite{Sorensen2013} shows that elderly people desire less spending in education while they are in support of more in health and pension.\footnote{\cite{Sorensen2013} uses cross-sectional survey data for 22 countries from the International Social Survey Program (ISSP). There are four Role of Government surveys corresponding to the years 1985, 1990, 1996 and 2006.} However, the author claims that these life-cycle effects are quite small. On the other hand, \cite{Busemeyer2009} find sizable age-related differences in public policy preferences.\footnote{\cite{Busemeyer2009} use cross-sectional survey data for 14 OECD countries from the 1996 ISSP Role of Government dataset.} Although both studies disagree on the magnitude of the conflict, they both claim that such a conflict exists. They also agree about the heterogeneity among countries of these life-cycle effects. \cite{Jager2016} also assess the impact of demographic aging on public investment.\footnote{\cite{Jager2016} use panel data of 19 OECD countries between 1971 and 2007.} They find a negative long-run relationship between both relying on the fact that older people discount more future payoffs with respect to young people.\footnote{See, for example, \cite{Harrison2002}; \cite{Read2004}. See also \cite{Huffman2017} for a more recent empirical study with a decomposition by characteristics of time discounting in old population.}
%
%%%% Politico-economic models
%%This paper relates to the literature on politico-economic models. This literature has started following the work of \cite{Lindbeck1987} on probabilistic voting. These models are useful to examine the relationship between redistribution policies and growth (see, for example, \citealt{Alesina1994}; \citealt{Persson1994}; \citealt{Krusell1997}). However, they are rather focused on intra-generational government budget allocation conflicts than inter-generational. Lately, some authors have brought these models back into use in order to analyze the age-related conflict between generations.
%% Lancia & Prarolo (2012)
%%\cite{Lancia2012} develop an overlapping generations (OLG) model with three types of agents: young, adult and old. They focus their analysis on economic growth and find that an increasing life expectancy is a growth-enhancing factor. Economic growth is determined by two components: human capital growth and total factor productivity growth. First, young agents inherit the average human capital level of their parents and decide to invest on their education level. The higher is the expected life expectancy, the greater is the incentive to educate. Investing in education increases human capital. Second, all agents vote to determine the innovation public policy that fosters total factor productivity. This investment is done at the cost of public pensions. Thus, elderly are necessary opposed to innovation. When both, young and adults, are net winners from public investment policy, they form a coalition in the political process to adopt such a policy. Therefore, aging has two opposite effects on growth. On one hand, it generates incentives to human capital accumulation and innovation. On the other hand, it increases the political weight of elderly who are against innovation and makes policies more difficult to implement.
%%% Gonzalez-Eiras and Niepel (2012)
%%With the same type of conflict on transfers to retired old households and public investment, \cite{Gonzalez-Eiras2012} analyze implications for per-capita growth. However, they also endogenize the retirement age in a politico-economic equilibrium. They distinguish two effects: a direct one through the savings rate, labor supply and capital accumulation ; and an indirect one through the age-related conflict within the public policy to determine the levels of taxes, government spending and retirement age. They predict an increase of tax rates and the retirement age in OECD countries to offset population aging and thereby boost per-capita growth.
%
%%% STEP 3 : Identify the gaps or the problems with previous research
%
%%Despite the existing literature on the relationship between demographic dynamics and growth, the impact of demography on the income allocation between capital and labor has been understudied. 
%% Schmidt and Vosen (2013)
%%To the best of my knowledge, \cite{Schmidt2013} is the only one paper to examine the impact of the demography on the labor share. Using an OLG model with pension system, they show that an aging population leads to more saving and so more capital. In a closed economy, the effect on the labor share depends on the value of the capital-labor elasticity of substitution. For an elasticity greater (resp. smaller) than unity, the effect is negative (resp. positive). While in a small economy with perfect capital mobility, they argue that households invest abroad because domestic interest rates fall. As a result, the increasing net foreign assets income shrinks the labor share. Their paper points out a link between the population aging and the labor share through capital accumulation. However, they do not consider any age-related conflict within the public budget allocation.
%
%% Caballero and Hammour (1998)
%%\cite{Caballero1998} incorporate the long-run response of firms to labor market institutions shaped in favor of workers. This response is the substitution of labor with capital. However, they do not look upstream to determine the reasons of such a labor market institutional context. In high-income countries, such as France and the United-States, the after-war period has been characterized by a colossal increase of the working-age population. Either with the so called baby-boomers cohort or the immigration. During the 1970s and the 1980s, this generation may have shaped the labor market institutions in their favor because they had enough political weight to do so. This period has been characterized by rising unionization, employment protection and unemployment benefits% (\textbf{graph?})
%%. All of these labor market institutions has raised real wages and therefore the labor cost for firms. In such a context, the argument of \cite{Caballero1998} fits perfectly. Firms have shifted from labor to capital in order to thwart workers empowerment.
